\documentclass[11pt, a4paper]{article}

% --- Packages ---
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry} % Sets 1-inch margins
\usepackage{amsmath, amssymb, amsthm} % For math symbols and environments
\usepackage{hyperref} % Adds clickable links to the Table of Contents
\usepackage{xcolor} % For custom colors
\usepackage{tcolorbox} % For beautiful note/definition boxes
\usepackage{graphicx} % For inserting images
\usepackage{booktabs} % For professional-looking tables

% --- Hyperref Setup ---
\hypersetup{
	colorlinks=true,
	linkcolor=blue,
	filecolor=magenta,      
	urlcolor=cyan,
	pdftitle={Course Notes},
}

% --- Custom Environments ---
% A nice blue box for definitions or key concepts
\newtcolorbox{conceptbox}[1]{
	colback=blue!5!white,
	colframe=blue!75!black,
	fonttitle=\bfseries,
	title=#1,
	arc=4mm % Rounded corners
}

% --- Document Information ---
\title{\textbf{Mathematics for Machine Learning}}
\author{Md Mehrab Hossain Khandoker}
\date{\today}

% --- Main Body ---
\begin{document}
	
	\maketitle
	\thispagestyle{empty} % Removes page number from the title page
	\newpage
	
	% --- Table of Contents ---
	\tableofcontents
	\newpage
	
	% --- Lecture 1 ---
	\section{Vectors, Vector Spaces and Vector Subspaces}
	\subsection{Vectors}
	The primitive idea of a vector is that, it is a quantity with magnitude and direction. But the abstract idea of a vector is that, it can be thought of as an ordered n-tuple. The way we interpret that, can be based on different applications of that vector. Suppose, we have a 5-component vector like, \[
	u = \begin{pmatrix}
		u_1 \\
		u_2 \\
		u_3 \\
		u_4 \\
		u_5
	\end{pmatrix}
	\]
	where each of the five components represent a health parameter of a patient. E.g. blood pressure, pulse rate etc. This idea is strictly tied to the application of the vector. In order to define the vector mathematically, we need an abstract concept of \textbf{`Field'}, that will lead us to the \textbf{`Vectors'}.
	\subsection{Field $\mathbb{F}$}
	The Field is a non-empty collection of elements with operations ($+$, $\cdot$) where $+$ is the Field Addition and $\cdot$ is the Field Multiplication, such that the following properties hold: 
	\begin{enumerate}
		\item There exists $0 \in \mathbb{F}$ such that for any $a \in \mathbb{F}$, $a + 0 = 0 + a = a$. $0$ is the Additive Identity element here.
		\item For any two elements $a,b \in \mathbb{F}$, $a + b \in \mathbb{F}$.
		\item There exists for every element $a \in \mathbb{F}$, the additive inverse $(-a) \in \mathbb{F}$, such that $a + (-a) = 0$.
		\item There exists $1 \in \mathbb{F}$ such that for any $a \in \mathbb{F}$, $a \cdot 1 = 1 \cdot a = a$. $1$ is the Multiplicative Identity element here.
		\item For any two elements $a,b \in \mathbb{F}$, $a \cdot b \in \mathbb{F}$.
		\item There exists for every element $a \in \mathbb{F}$, the Multiplicative inverse $a^{-1} \in \mathbb{F}$, such that $a \cdot a^{-1} = a^{-1} \cdot a = 1$.
	\end{enumerate}
	
	\begin{conceptbox}{Important Definition}
		This is a custom callout box. Use it to highlight formulas, definitions, or critical exam topics so they stand out when you review.
	\end{conceptbox}
	
\end{document}